Turbulence in compact to giant H~II regions

### 2023-04-21 strucfunc_paper.tex
Nearly finished 30 Dor revision. All except comparison with previous

The 30 Doradus (Tarantula Nebula) nebula is located at a distance of \SI{49.9}{kpc} \citetext{\SI{1}{\arcsecond} = \SI{0.24}{pc} ; \citealp{2013Natur.495...76P}}.
It is a luminous star-forming region in the LMC (Large Magellanic Cloud) and is the most luminous complex in the Local Group \citep{1984ApJ...287..116K}.
The central ionized region spans for \SI{40}{pc} and host the massive dense star cluster R136
with ionizing output \(Q_0\) of is \SI{e51.40}{photons.s^{-1}} \citep{2020MNRAS.499.1918B} and the luminosity in \ha{} of \SI{e39.46}{erg.s^{-1}} (194 times higher compared to the Orion Nebula).
%\citep{1991IAUS..148..145W}. %Note: check the bibliographic format
The mean non-thermal linewidth in \ha{} is \SI{22}{km.s^{-1}} \citep{2013A&A...555A..60T}.
It host the active star forming region NGC 2070 \citep{2013AJ....145...98W} where the star-formation rate has recently peaked \citep{2015ApJ...811...76C} and host a population of OB and WR stars \citep{2011A&A...530A.108E}.
This nebula is commonly used as a comparison for extragalactic star-forming regions.

@@

The 30~Doradus structure function is shown in Figure~\ref{fig:strucfunc-fit-MC}a.
The value of the observed \(\sigma\pos^2 = \SI{252}{km^{2}.s^{-2}}\) is obtained at \(r_0 = \SI{3}{pc} \) (the derived values from our model are \(\sigma\pos^2 = \SI{297}{km^{2}.s^{-2}}\) and \(r_0 = \SI{4}{pc} \)).
The observed value of \(2\sigma\pos^2\) corresponds to \(r = \SI{13}{pc} \).
The maximum \(B(r)\) value correspond to \SI{654}{km^{2}.s^{-2}} at \(r = \SI{21}{pc}\).
From this value the \(B(r)\) values decrease and it is possible to observe a downturn in the structure function from to \SI{250}{km^{2}.s^{-2}} at \(r =  \SI{38}{pc}\) following the tapered fluctuations behavior.
The seeing (RMS) value derived for this regions is \SI{0.16}{pc} (\(s_0\)=\SI{1.5}{\arcsecond}) and just one point of the structure function is below this value.
Considering the first point above this \(s_0\) value to be valid, which corresponds to \SI{15}{km^{2}.s^{-2}} at \(r = \SI{0.2}{pc} \) the slope for \(\sigma\pos^2\) and \(2\sigma\pos^2\) we obtain \num{1.04} and \num{0.84}, respectively, while our derived value is \num{0.85}.

>>>>

The giant \hii{} region 30~Doradus (Tarantula Nebula) is located at a distance of \SI{49.9}{kpc} \citetext{\SI{1}{\arcsecond} = \SI{0.24}{pc} ; \citealp{2013Natur.495...76P}}.
It is a luminous star-forming region in the LMC (Large Magellanic Cloud) and is the most luminous complex in the Local Group \citep{1984ApJ...287..116K}.
The star cluster that energizes the region is NGC~2070, with a central core (known as R136)
with ionizing luminosity \(Q_0 = \SI{e51.40}{photons.s^{-1}}\)  \citep{2020MNRAS.499.1918B},
which produces an \ha{} luminosity of \SI{e39.46}{erg.s^{-1}} (200 times the Orion Nebula)
for the central ionized region of size \SI{40}{pc}.
The mean non-thermal linewidth in \ha{} is \SI{22}{km.s^{-1}} \citep{2013A&A...555A..60T}.
Star formation is still ongoing in NGC~2070 \citep{2013AJ....145...98W},
although the star-formation rate peaked about \SI{4}{Myr} ago
\citep{2015ApJ...811...76C} and it currently hosts some of the most massive stars known
\citep{Kalari:2022p}
and several Wolf-Rayet stars \citep{2011A&A...530A.108E}.
This nebula is commonly used as a comparison for extragalactic star-forming regions.

@@

The 30~Doradus structure function is shown in Figure~\ref{fig:strucfunc-fit-MC}a.
The model-derived parameters are \(\sigma\pos^2 = \SI{297 \pm 40}{km^{2}.s^{-2}}\),
\(r_0 = \SI{4\pm 1}{pc} \)), and \(m = 0.85 \pm 0.1\).  The empirically-derived variance is about
15\% smaller, indicative of a moderate finite-box effect. On either measure,
the region is a clear outlier in our sample, with a value of \(\sigma\pos^2\) that is
more than three times larger than any other of our regions,
as can be graphically appreciated from the velocity histograms in Figure~\ref{fig:pdfs}.

At scales larger than the correlation length, the structure function has a maximum
at \(r = \SI{20}{pc}\) and then falls at the largest scales.
This behavior is similar to that seen in the Orion Nebula and might
likewise be evidence for a decline of the fluctuation amplitude towards the outskirts.
On the other hand, the sharp upward turn towards the maximum in \(B(r)\) is more reminiscent
of the expectations for a periodic fluctuation (Figure~\ref{fig:model-strucfunc}b),
in which case the wavelength would be of order the size of the map.
Evidence for such a pattern can be seen directly in the velocity map
(Figure~\ref{fig:velocity-maps}) as a red-blue asymmetry between the south-east
and north-west, which is also seen in the kinematics of the O~stars
\citep{Henault-Brunet:2012h}
and has been interpreted as evidence for rotation of the cluster.
